% -*- TeX-master: "main"; fill-column: 72 -*-

\section{Background}  \label{background} 

\subsection{Motivation}

Computational modeling is an increasingly interdisciplinary field. Different aspects of the modeling activity come together, that need information to be stored in a cohesive unit. When sharing a model, not exchanging all relevant files might cause problems. Several different approaches have been tried to solve this issue, such as folder based project structures, or special versions of version control systems. Unfortunately these approaches are not as easy to support for tool authors as a single file based solution would. 

This specification describes \textit{COMBINE archive}, a file that contains all the information needed to describe a modeling and simulation experiment. The \textit{COMBINE archive} is encoded with the \emph{Open Modeling Exchange format} (OMEX).A \textit{COMBINE archive} is a single file containing the various documents (and possibly in the future, references to documents), necessary for the description of a model and all associated datasets and procedures. This includes for instance, but not limited to, simulation experiment descriptions in SED-ML, all models needed to run the simulations in SBML or CellML
and their graphical representations in SBGN-ML. 

The COMBINE archive aims to augment these efforts by standardizing a manifest that describes all files in the archive, guidance for encoding metadata and a convention for bundling the information together. Such an approach also allow resources using a distributed version control system (such as PMR2, \url{http://models.cellml.org/}) to export COMBINE archives, by generating a manifest file during export. 
http://models.cellml.org/
Details of earlier independent proposals are provided below. 

\subsection{History}

The COMBINE archive was engendered from the SED-ML archive, that was first introduced in the SED-ML mailing list in 2009, and briefly described in SED-ML Level~1 Version~1 \citep{Waltemath:2011}. The SED-ML archive addressed the need of providing a way to include all relevant models used in a SED-ML simulation experiment along with the experiment specification. The SED-ML archive is basically the convention to provide, inside a ZIP file (with extension .sedx), a SED-ML document with the same base name as the archive and all models listed in the SED-ML file. 

This specification has been created out of the many discussions that took place
on the combine-discuss mailing list. The primary threads are located here: 

\begin{itemize}
	\item \href{http://listserver.ebi.ac.uk/pipermail/combine-discuss/2011-October/thread.html}{http://listserver.ebi.ac.uk/pipermail/combine-discuss/2011-October/thread.html}
	\item \href{http://listserver.ebi.ac.uk/pipermail/combine-discuss/2011-November/000016.html}{http://listserver.ebi.ac.uk/pipermail/combine-discuss/2011-November/000016.html}
	\item \href{http://listserver.ebi.ac.uk/pipermail/combine-discuss/2012-January/thread.html}{http://listserver.ebi.ac.uk/pipermail/combine-discuss/2012-January/thread.html}
\end{itemize}

The discussion continued at the last Hackathons, HARMONY 2012 where for the first time a larger audience discussed a preliminary proposal put together by Richard Adams, Frank T. Bergmann and Nicolas Le Nov\`{e}re \citep{Adams:2012}.  
Further discussions were held at HARMONY 2013.\\ (\url{https://docs.google.com/document/d/1ji2mOiWzXXl9ON6sU6Svd3E_IufowUCz24hklqci0iM/edit}). 

Discussions about the development of OMEX and the COMBINE archive are now taking place on the combine-archive Google group (\url{https://groups.google.com/forum/?#!forum/combine-archive}).
